---
title: "Alcohol vs Seat choice"
author: "Syi-yonnie Richard"
date: "Fall 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

  
## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

  As we can see the column plot, the difference between the front and back row appear to have an huge gap, while the back and middle only have an big gap.. but not compared to the huge gap between front and back row.

## Numerical Summarys 
```{r}
favstats(alcohol~Seat,data=ucdavis1)
```

  The chart confirms that the back row drinks 8.5 more drinks than the middle row while drinking 3.3 drinks per week, also the front row drinks 1.7 per week. All three rows don't consume the same amount of drinks proved by the columns and information. 

## Inferential Tests
```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```
  P value represent the chances of getting an result of what we already obtained. I do not agree with the null hypothesis due to it being small/less.
  
```{r}
plot(TukeyHSD(model1))
```

Based of the plot, it shows the front and middle are not different even though the front and back/back and middle appear to be different.
## Conclusions

In conclusion we determined anova had to be used in order to determine the amount of drinks per week like the first category.
The chart confirms that the back row drinks 8.5 more drinks than the middle row while drinking 3.3 drinks per week, also the front row drinks 1.7 per week. All three rows don't consume the same amount of drinks proved by the columns and information. P value represent the chances of getting an result of what we already obtained. I do not agree with the null hypothesis due to it being small/less.

